---
title: "iST vs SP3"
author: "Fabio Bedin | MS-Unit"
output: html_document
---

```{r librerie, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.align = "center", warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10)
library("MBQN")
library("dplyr")
library("tidyr")
library("DEP")
library("SummarizedExperiment")
library("preprocessCore")
library("tibble")
library("ggplot2")
library("enrichR")
library("DT")
library("stringr")
library("patchwork")
library("here")
library("datapasta")
library("ggstatsplot")
library("UpSetR")
library("ggrepel")
```

```{r Custom Functions}

source(here::here("code/custom_functions.R"))

```

## Introduction {.tabset .tabset-fade .tabset-pills}

***
scrivere qualcosa...

```{r input_Data}
data <- read.csv(here::here("data/proteinGroups_iST_SP3_HpH_Add_on.txt"), header = TRUE,stringsAsFactors = FALSE, sep = "\t")

data <- data[data$Reverse != "+" & data$Potential.contaminant != "+" & data$Only.identified.by.site != "+",]

data_unique <- make_unique(data, "Gene.names", "Protein.IDs", delim = ";")
```

### Titration iST vs SP3 {.tabset .tabset-fade}

In this analysis I compare the different number of protein identify in the two conditions **iST** and **iST + SP3** taking into account the different concentrations used: *0.1ug*, *1ug* and *5ug*.

```{r exp_1}
expdesign <- read.table(here::here("data/expdesign_2.tsv"), header = T, stringsAsFactors = F)

conditions<-c("Ist_01ug", "Ist_1ug", "Ist_5ug", "SP3_01ug", "SP3_1ug", "SP3_5ug")
#conditions<-c("Fractination_8_iST", "Fractination_6_iST", "Fractination_3_iST_AddOn")

expdesign <- subset(expdesign, condition %in% conditions)

columns<-match(paste("Intensity.",expdesign$label,sep=""),colnames(data_unique))

Titration <- make_se(data_unique, columns, expdesign)
```

#### Protein per sapmle

```{r plot_numb_1, warning=FALSE,fig.height = 13, fig.width = 15}
plot_numbers_lables(Titration, sub_title = "Titration", lab_size = 10)
```

#### Distibution of each sample

```{r plot_norm_1, fig.height = 10, fig.width = 10}
plot_normalization(Titration)
```
 
```{r}
# data_unique %>%
#   as.data.frame() %>%
#   select(starts_with(c("name", "Intensity."))) %>%
#   select(starts_with("name") | contains("ug") & !contains("AddOn") & !contains("HpH")) %>% 
#   pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
#   mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
#   group_by(samples) %>% 
#   summarize(n = n(), sum = sum(intensity)) %>% 
#   mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
#   mutate(condition = gsub(pattern = "_[[:digit:]]$", replacement = "", samples)) %>% 
#   ggplot( mapping = aes(x = samples, y = sum, fill = condition)) +
#     geom_col() +
#     geom_text(aes(label=sum), size=5, position = position_stack(vjust = 0.5))+
#     labs(title = "Titration", x = "",y = "Number of proteins") +
#     theme_DEP2() + 
#     theme(plot.subtitle = element_text(size = 16, face = "bold", hjust = 0.5), plot.title = element_text(size = 20)) +
#     labs(x = NULL, subtitle = "Protein per sample") 
```

#### Upset plot 0.1ug

```{r up_1, fig.height = 13, fig.width = 15}
define_set <- c("iST_01ug_1", "iST_01ug_2", "iST_01ug_3","SP3_01ug_1", "SP3_01ug_2", "SP3_01ug_3")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("ug") & !contains("AddOn") & !contains("HpH")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 6,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 3),
        main.bar.color  = "gray44")
  
```

#### Upset plot 1ug

```{r up_2, fig.height = 13, fig.width = 15}
define_set <- c("iST_1ug_1", "iST_1ug_2", "iST_1ug_3", "SP3_1ug_1", "SP3_1ug_2", "SP3_1ug_3")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("ug") & !contains("AddOn") & !contains("HpH")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 6,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 3),
        main.bar.color  = "gray44")
  
```

#### Upset plot 5ug

```{r up_3, fig.height = 13, fig.width = 15}
define_set <- c("iST_5ug_1", "iST_5ug_2", "iST_5ug_3", "SP3_5ug_1", "SP3_5ug_2", "SP3_5ug_3")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("ug") & !contains("AddOn") & !contains("HpH")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 6,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 3),
        main.bar.color  = "gray44")
  
```

### Titration **LCM** iST vs SP3 {.tabset .tabset-fade}

In this analysis I compare the different number of protein identify in the two conditions **LCM-iST** and **LCM-iST + SP3** taking into account the different cells used: *1000*, *500*, *250* *125* and *50*.

```{r exp_2}
expdesign <- read.table(here::here("data/expdesign_2.tsv"), header = T, stringsAsFactors = F)

conditions<-c("LCM_iST_1000", "LCM_iST_500", "LCM_iST_250", "LCM_iST_125", "LCM_iST_50",
              "LCM_SP3_1000", "LCM_SP3_500", "LCM_SP3_250", "LCM_SP3_125", "LCM_SP3_50")
#conditions<-c("Fractination_8_iST", "Fractination_6_iST", "Fractination_3_iST_AddOn")

expdesign <- subset(expdesign, condition %in% conditions)

columns<-match(paste("Intensity.",expdesign$label,sep=""),colnames(data_unique))

Titration <- make_se(data_unique, columns, expdesign)
```

#### Protein per sapmle

```{r plot_numb_2, warning=FALSE,fig.height = 13, fig.width = 15}
plot_numbers_lables(Titration, sub_title = "Titration LCM", intercept = F, lab_size = 10)
```

#### Distibution of each sample

```{r plot_norm_2, message=FALSE, fig.height = 10, fig.width = 10}
plot_normalization(Titration)
```
 
#### Upset plot 1000

```{r up_1.1, fig.height = 13, fig.width = 15}
define_set <- c("iST_1000_LMC_1", "iST_1000_LMC_2", "SP3_1000_LMC_1", "SP3_1000_LMC_2")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("LMC")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 4,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 2),
        main.bar.color  = "gray44")
  
```

#### Upset plot 500

```{r up_2.1, fig.height = 13, fig.width = 15}
define_set <- c("iST_500_LMC_1", "iST_500_LMC_2", "SP3_500_LMC_1", "SP3_500_LMC_2")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("LMC")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 4,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 2),
        main.bar.color  = "gray44")
  
```

#### Upset plot 250

```{r up_3.1, fig.height = 13, fig.width = 15}
define_set <- c("iST_250_LMC_1", "iST_250_LMC_2", "SP3_250_LMC_1", "SP3_250_LMC_2")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("LMC")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 4,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 2),
        main.bar.color  = "gray44")
  
```

#### Upset plot 125

```{r up_4.1, fig.height = 13, fig.width = 15}
define_set <- c("iST_125_LMC_1", "iST_125_LMC_2", "SP3_125_LMC_1", "SP3_125_LMC_2")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("LMC")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 4,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 2),
        main.bar.color  = "gray44")
  
```

#### Upset plot 50 cells

```{r up_5.1, fig.height = 13, fig.width = 15}
define_set <- c("iST_50_LMC_1", "iST_50_LMC_2", "SP3_50_LMC_1", "SP3_50_LMC_2")

data_unique %>%
  as.data.frame() %>%
  select(starts_with(c("name", "Intensity."))) %>%
  ## define combination of interest in the original dataset
  select(starts_with("name") | contains("LMC")) %>% 
  pivot_longer(!name, names_to = "samples", values_to = "intensity") %>% 
  mutate(intensity = if_else(intensity == 0, 0, 1)) %>% 
  mutate(samples = gsub(pattern = "^.*\\.", replacement = "", samples)) %>% 
  pivot_wider(names_from = samples, values_from = intensity) %>% 
  as.data.frame() %>% 
  upset(nsets = 4,
        sets = define_set,
        #order.by = "degree",
        order.by = "freq",
        keep.order = T,
        text.scale = 2.5,
        point.size = 4,
        line.size = 0.5, 
        sets.bar.color = rep(c("coral2", "turquoise3"), each = 2),
        main.bar.color  = "gray44")
  
```


